### 2014-12-30 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update to report

To calculate the total fire size, the appropriate burning area (exposed wood area) of the basement needed to be determined. Based on the floor plan of the structure,

The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS. The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations (1 source in the basement bathroom and 1 source in the basement kitchen).

Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made. The first assumption is that the fires start at the beginning of the simulation and increase to a value of 8.5~MW in 10~s. The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS. Since the actual ignition time is unknown, the fire was ramped quickly to reflect the conditions determined from reports and post-incident images. The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations in the basement (1 source for the kitchen, 1 source for the bathroom).  At 207~s, using a simple decay model, the fire size decreases lineraly to 25~\% of its peak value in 60~s. This is to account for the impact of firefighters putting water on the basement fire (Table~\ref{tab:fire_info}). The following lines define the source fires in the FDS input file:

@@

Figure~\ref{fig:hrr} shows the overall prescribed design fire for this scenario, which is the sum of the HRRs of the three source fires. In this figure, the text labels the prescribed steady peak HRR and the decay phase associated with firefighter water application. Therefore, the estimated maximum specified fire size for this structure was approximately 8.25~MW. Note that the prescribed HRR can be different than the simulated HRR calculated by FDS based on the amount of available fuel, oxygen, and ventilation. A comparison of the prescribed HRR and the simulated HRR is discussed in Section~\ref{HRR}.

>>>>

To calculate the total fire size, the appropriate burning area of the basement needed to be determined. Based on the floor plan of the structure and post-incident images, two distinct fires were considered: 1 source in the basement bathroom and 1 source in the basement kitchen.

Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made. The fires started at the beginning of the simulation and increased to a value of 8.5~MW in 10~s. The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS. Since the actual ignition time is unknown, the fire was ramped quickly to reflect the conditions determined from reports and post-incident images. The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations in the basement (1 source for the kitchen, 1 source for the bathroom).  At 207~s, using a simple decay model, the fire size decreases lineraly to 25~\% of its peak value in 60~s. This is to account for the impact of firefighters putting water on the basement fire (Table~\ref{tab:fire_info}). The following lines define the source fires in the FDS input file:

@@

Figure~\ref{fig:hrr} shows the overall prescribed design fire for this scenario, which is the sum of the HRRs of the three source fires. In this figure, the text labels the prescribed steady peak HRR and the decay phase associated with firefighter water application. Therefore, the estimated maximum specified fire size for this structure was approximately 8.5~MW. Note that the prescribed HRR can be different than the simulated HRR calculated by FDS based on the amount of available fuel, oxygen, and ventilation. A comparison of the prescribed HRR and the simulated HRR is discussed in Section~\ref{HRR}.
